B\'{e}zier $\bar{B}$ projection

### 2018-02-15 projection1120.tex
Revisions.

\begin{abstract}
  In this paper we demonstrate the use of B\'{e}zier projection to alleviate locking phenomena in structural mechanics applications of isogeometric analysis. \added{Interpreting the well-known $\bar{B}$ projection in two different ways we develop two formulation for locking problems in beams and nearly incompressible elastic solids.  One formulation leads to a sparse symmetric symmetric system and the other leads to a sparse non-symmetric system.} To demonstrate the utility of the \added{\Bezier projection} for both geometry and material locking phenomena we focus on transverse shear locking in Timoshenko beams and volumetric locking in nearly compressible linear elasticity although the approach can be applied generally to other types of locking phenemona as well. B\'{e}zier projection is a local projection technique with optimal approximation properties, which in many cases produces solutions that are comparable to global $L^2$ projection. In the context of $\bar{B}$ methods, the use of B\'ezier projection produces sparse stiffness matrices with only a slight increase in bandwidth when compared to standard displacement-based methods. Of particular importance is that the approach is applicable to any spline representation that can be written in B\'ezier form like NURBS, T-splines, LR-splines, etc. We discuss in detail how to integrate this approach into an existing finite element framework with minimal disruption through the use of B\'ezier extraction operators and a newly introduced dual \added{basis for} the \Bezier \added{projection} operator. We then demonstrate the behavior of the two proposed formulations through several challenging benchmark problems.
\end{abstract}
\keywords{Isogeometric analysis, B\'ezier extraction, \added{\Bezier dual basis}, B\'ezier projection, $\bar{B}$-projection, locking}
\section{Introduction}
Isogeometric analysis (IGA), introduced by Hughes et al. \cite{hughes_isogeometric_2005}, adopts the spline basis, which underlies the CAD geometry, as the basis for analysis. Of particular importance is the positive impact of smoothness on numerical solutions, where, in many application domains, IGA outperforms classical finite elements~\cite{cottrell_isogeometric_2009,cottrell_studies_2007,cottrell2006isogeometric,hughes_duality_2008,bazilevs_isogeometric_2010,evans_n-widths_2009}. Initial investigations of IGA focused on non-uniform rational B-splines (NURBS) due to their dominance in commercial CAD packages. However, many advances are being made in analysis-suitable geometry representations that overcome the strict rectangular topological restrictions of NURBS. Examples include T-splines~\cite{bazilevs_isogeometric_2010,sederberg_t-splines_2003} and their analysis-suitable restriction~\cite{scott_local_2012, li_analysis-suitable_2013}, hierarchical B-splines~\cite{bornemann_subdivision-based_2013,scott_isogeometric_2014,schillinger_isogeometric_2012,evans_hierarchical_2015,forsey_hierarchical_1988}, and locally refined B-splines~\cite{dokken_polynomial_2013,johannessen_isogeometric_2014} among others.

@@

\added{In this paper we introduce two methods that employ \Bezier projection to produce a localized approximation to the standard $\bar{B}$ method. The motivation behind these methods is the fact that $\bar{B}$ methods result in dense linear systems when used in the context of smooth higher-order basis functions, for example NURBS or other splines. The methods we introduce result in a sparse linear system irrespective of the choice of basis functions. We call these methods the symmetric and non-symmetric \Bezier $\bar{B}$ projection methods, where the names indicate the symmetry of the resulting stiffness matrix. We show that both methods result in a sparse stiffness matrix and reduce locking. We also show that optimal convergence rates are achieved in the case of the non-symmetric method and near optimal convergence rates are achieved in the case of the symmetric method.  We also perform an inf-sup analysis of these methods.}

@@

\subsection{Symmetric \Bezier $\bar{B}$ projection}
\label{sec:symmetric-projection}
{\color{blue}Locking is caused in Timoshenko beam problems by the transverse shear. To reduce the effects of locking for these problems the $\bar{B}$ method projects the shear strain, $\gamma$, onto a lower order function space. This process produces a projected shear strain, which we call $\bar{\gamma}$,  that is substituted into the weak form of the problem statement. In this section we use the \Bezier projection operator to compute an approximation of $\bar{\gamma}$, and refer to this approach as the symmetric \Bezier $\bar{B}$ projection method because the resulting stiffness matrix is symmetric.}

@@

Localizing to the B\'{e}zier element we define the strain-displacement arrays in terms of element Bernstein basis functions of degree $p$ and $p-1$ as
\begin{align}
	\mathbf{B}_e^\kappa 
    	&= \begin{bmatrix} 0 & -{B^e_{0,p}}' & \cdots & 0 & -{B^e_{p,p}}' \end{bmatrix}, \\
    \mathbf{B}_e^\gamma
    	&= \begin{bmatrix} {B^e_{0,p}}' & -B^e_{0,p} & \cdots & {B^e_{p,p}}' & -B^e_{p,p} \end{bmatrix}, \\
    \bar{\mathbf{B}}_e
    	&= \begin{bmatrix} \bar{B}^e_{0,p-1} & \cdots & \bar{B}^e_{p-1,p-1} \end{bmatrix},
\end{align}
\added{where $B^e_{i,p}$ is the $i^{th}$ Bernstein basis function of order $p$}. We can then compute the element arrays as
\begin{align}
\mathbf{K}_e^b &= EI\mathbf{C}^e\langle{{\mathbf{B}_e^\kappa}^T,\mathbf{B}_e^\kappa}\rangle(\mathbf{C}^e)^T, \label{eq:symmetric_timoshenko}\\
\bar{\mathbf{M}}_e &= s{GA}\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\bar{\mathbf{B}}_e}\rangle(\bar{\mathbf{C}}^e)^T, \\
{\hat{\mathbf{P}}_e} &= \langle{(\hat{\bar{\mathbf{N}}}^e)^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T,
\end{align}
where $\mathbf{C}^e$ is the element extraction operator for the degree $p$ spline space, $\bar{\mathbf{C}}^e$ is the element extraction operator for the degree $p-1$ spline space, and $\hat{\bar{\mathbf{N}}}^e$ are the dual basis functions restricted to the element for the degree $p-1$ spline space. The global stiffness matrix can then be written as
\begin{align}
	\mathbf{K} = \mathbf{K}^b + \bar{\mathbf{K}}^s_S \label{eqn:symmetric_b_bar_timoshenko_stiffness}
\end{align}
where
\begin{align}
	\mathbf{K}^b &=\A_e\mathbf{K}_e^b,\label{eqn:bending_stiffness} \\
	\bar{\mathbf{K}}^s&={\hat{\mathbf{P}}}^T\bar{\mathbf{M}}{\hat{\mathbf{P}}}\label{eqn:shear_stiffness} \\
	{\hat{\mathbf{P}}} &=\A_e{\hat{\mathbf{P}}_e} \\
    \bar{\mathbf{M}} &=\A_e\bar{\mathbf{M}}_e
\end{align}
and $\A$ is the standard finite element assembly operator \cite{hughes_finite_2012}. We note that the assembly of $\bar{\mathbf{K}}^s$ requires the assembly of two intermediate matrices, $\bar{\mathbf{M}}$ and ${\hat{\mathbf{P}}}$. The computation of these matrices is needed because the product of two integrals over the entire domain can not be localized to the element level.
\subsection{Non-symmetric \Bezier $\bar{B}$ projection}
\label{sec:non-symmetric}

\added{Simo and Hughes \cite{hughes_variational_1986} have shown that $\bar{B}$ formulations and mixed formulations are equivalent. However, the development of the symmetric \Bezier $\bar{B}$ projection method presented in Section~\ref{sec:symmetric-projection}, where we began by considered the $\bar{B}$ formulation as a strain projection method, lacks a connection to mixed formulations. In this section we present a second method based on \Bezier projection in which we view the $\bar{B}$ formulation as a mixed formulation where, for the Timoshenko beam problem, the auxiliary variable is the shear strain.  In this method we use the \Bezier dual basis functions as the test functions for the auxiliary variable. Once the problem has been cast as a mixed formulation we then eliminate the auxiliary variable to get a purely displacement based formulation. This method preserves convergence rates and all assembly routines of the stiffness matrix can be performed at the element level, but it does lead to a non-symmetric stiffness matrix.}

\subsubsection{The weak form}
\added{In the mixed formulation for the Timoshencko beam problem the shear stress, $\tau=sGA\gamma$, is taken as a new independent variable. The weak form of the mixed formulation problem is then stated as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ and $\tau\in{L}^2(\Omega)$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$ and $\delta\tau\in{L}^2(\Omega)$}
\begin{align}
    \int_{0}^L\kappa(\mathbf{w})EI\kappa(\mathbf{u}) + {\gamma}(\mathbf{w})\tau \, dx&= l\langle{\mathbf{w}}\rangle\\
    \int_{0}^L\delta\tau(sGA\gamma(\mathbf{u})-\tau) \, dx &= 0.
\end{align}
\subsubsection{Discretization}
\added{In the finite element formulation of the mixed problem the discretization of $\mathbf{u}$ and $\mathbf{w}$ remain the same. The shear strain and its variation, however, are in $L^2(\Omega)$, so their finite element approximation can be made from functions with lower regularity, such as discontinuous polynomials. When the field $\mathbf{u}$ is discretized by $p^{th}$ degree spline basis functions defined by the knot vector given in \eqref{eq:origin_knot_vector}, we chose the $p-1^{th}$ degree spline basis functions defined by the knot vector given in \eqref{eq:projected_knot_vector} to discretize the shear stress $\tau$ and the corresponding dual basis to discretize its variation $\delta\tau$. The discrete form of the shear stress and its variation are given by}
\begin{align}
    \tau&=\sum_A\tau_A\bar{N}_A \\
    \delta\tau&=\sum_A\delta\tau_A\hat{\bar{N}}_A.
\end{align}
\added{The stiffness matrix for the mixed form can then be written as}
\begin{equation}
   \mathbf{K}_{mix} =  
    \begin{bmatrix}
        \mathbf{K}^b & \mathbf{P}^T \\
        sGA\hat{\mathbf{P}} & -\mathbf{I}
    \end{bmatrix}
    \label{eq:mixed_timoshenko}
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e,
\end{equation}
\added{and}
\begin{equation}
    \mathbf{P}_e=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
\added{We can now eliminate the control variable of the shear stress from \eqref{eq:mixed_timoshenko} to get a pure displacement formulation where the stiffness matrix can be written as}
\begin{equation}
    \mathbf{K}=\mathbf{K}^b+\bar{\mathbf{K}}^s_{NS}, 
\end{equation}
where 
\begin{equation}
    \bar{\mathbf{K}}^s_{NS}=sGA\mathbf{P}^T\hat{\mathbf{P}}.
    \label{eq:nonsymmetric_timoshenko}
\end{equation}
\added{We can see that use of different function spaces for the shear strain and its variation leads to a non-symmetric stiffness matrix.}

\paragraph{Remark} \added{ The symmetric \Bezier $\bar{B}$ formulation is not consistent with a mixed formulation. To see this we can recover the mixed formulation of \eqref{eqn:symmetric_b_bar_timoshenko_stiffness}, which is}
\begin{equation}
    \begin{bmatrix}
        \mathbf{K}^b & \hat{\mathbf{P}}^T \\
        sGA\hat{\mathbf{P}} & -\bar{\mathbf{M}}^{-1}
    \end{bmatrix},
\end{equation}
\added{where both the shear stress and its variation are discretized by the dual basis functions. However, for the inner product of dual basis functions we have}
\begin{equation}
    \langle{\hat{\bar{N}}_i,\hat{\bar{N}}_j}\rangle\neq{\bar{\mathbf{M}}^{-1}_{ij}},
\end{equation}
\added{which shows the inconsistency between the symmetric \Bezier $\bar{B}$ formulation and the mixed formulation.}

@@

\section{Volumetric locking: Nearly incompressible linear elasticity}
\label{sec:nearlyincompressible}
To demonstrate the use of \Bezier $\bar{B}$ {methods} to alleviate volumetric locking effects we study the nearly incompressible elasticity problem in two dimensions. We start with the small strain tensor $\boldsymbol{\varepsilon}$, which is defined as the symmetric part of the displacement gradient, i.e., 
\begin{equation}
\varepsilon_{ij}=\dfrac{u_{i,j}+u_{j,i}}{2}.
\end{equation}
The stress tensor is related to the strain tensor through the generalized Hooke's law
\begin{equation}
\sigma_{ij}=c_{ijkl}\varepsilon_{kl}
\end{equation}
where, for isotropic elasticity, the elastic coefficients and stress tensor can be expressed in terms of the Lam\'{e} parameters $\lambda$ and $\mu$ as
\begin{align}
c_{ijkl} &=\mu(\delta_{ik}\delta_{jl}+\delta_{il}\delta_{jk})+\lambda\delta_{ij}\delta_{kl}\\
\sigma_{ij} &= \lambda\varepsilon_{kk}\delta_{ij} + 2\mu\varepsilon_{ij}.
\end{align}
The Lam\'e parameters $\lambda$ and $\mu$ are defined in terms of Young's modulus, $E$, and Poisson's ratio, $\nu$, as
\begin{align}
\lambda &=\dfrac{\nu{E}}{(1+\nu)(1-2\nu)}\\
\mu &=\dfrac{\nu{E}}{2(1+\nu)}.
\end{align}
we can write the strong form of linear elasticity as
\begin{align}
	\sigma_{ij,j}+f_i &= 0 \text{ in $\Omega$} \\
    u_i &= g_i\text{ on $\Gamma_{g_i}$} \\
    \sigma_{ij}n_j &= h_i\text{ on $\Gamma_{h_i}$}
\end{align}
where Dirichlet boundary conditions are applied on $\Gamma_{g_i}$, Neumann boundary conditions are applied on $\Gamma_{h_i}$, and the closure of the domain $\Omega$ is $\bar{\Omega}=\Omega\cup\Gamma_{g_i}\cup\Gamma_{h_i}$. \added{To desmonstrate the source of volumetric locking, we introduce the pressure term}
\begin{equation}
    p=-(\lambda+2\mu/3){\epsilon}_{ii}.
\end{equation}
If $\nu\rightarrow\dfrac{1}{2}$ then $\lambda$ becomes very large and \added{an additional constraint is applied to the volumetric strain as}
\begin{equation}
    {\epsilon}_{ii}=0.
\end{equation}
\subsection{Symmetric \Bezier $\bar{B}$ projection}
\subsubsection{The weak form}
The $\bar{B}$ approach for nearly incompressible linear elasticity splits the strain tensor $\varepsilon$ into volumetric and deviatoric strains and then replaces the volumetric strain with a projected strain. We begin with
\begin{equation}
\boldsymbol{\varepsilon}(\mathbf{u})=\boldsymbol{\varepsilon}^{vol}(\mathbf{u})+\boldsymbol{\varepsilon}^{dev}(\mathbf{u})
\end{equation}
where $\boldsymbol{\varepsilon}^{vol}=\dfrac{1}{3}\mathrm{tr}(\boldsymbol{\varepsilon})\mi$ is the volumetric strain and $\boldsymbol{\varepsilon}^{dev}=\boldsymbol{\varepsilon}-\dfrac{1}{3}\mathrm{tr}(\boldsymbol{\varepsilon})\mi$ is the deviatoric strain. The volumetric strain is then replaced by a projected volumetric strain $\bar{\boldsymbol{\varepsilon}}^{vol}$ and the new total strain becomes
\begin{equation}
\bar{\boldsymbol{\varepsilon}}=\bar{\boldsymbol{\varepsilon}}^{vol}+\boldsymbol{\varepsilon}^{dev}.
\end{equation}
The weak form can then be written as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$
\begin{equation}
    \bar{a}\langle{\mathbf{w},\mathbf{u}}\rangle=\bar{l}\langle{\mathbf{w}}\rangle
\end{equation}
where
\begin{align}
    \bar{a}\langle{\mathbf{w},\mathbf{u}}\rangle&=\int_{\Omega}\bar{\epsilon}_{ij}(\mathbf{w})c_{ijkl}\bar{\epsilon}_{kl}(\mathbf{u})d\Omega, \\
    \bar{l}\langle{\mathbf{w}}\rangle&=\int_{\Omega}\mathbf{w}\cdot\mathbf{f}d\Omega+\int_{\Gamma_{h}}\mathbf{w}\cdot\mathbf{h}d\Gamma.
\end{align}

@@

We have presented two B\'{e}zier $\bar{B}$ projection methods, which we have called symmetric and non-symmetric \Bezier $\bar{B}$ projection, as an approach to overcome locking phenomena in structural mechanics applications of isogeometric analysis while maintaining sparsity of the resulting linear system. The methods utilize B\'ezier extraction and projection, which makes it simple to implement them in an existing finite element framework and makes it applicable to any spline representation which can be written in \Bezier form. In contrast to global $\bar{B}$ methods, which produce dense stiffness matrices, the B\'ezier $\bar{B}$ approach results in a sparse stiffness matrix while still benefiting from higher-order convergence rates. \added{We have made the connection between the non-symmetric method and a mixed formulation and shown that, although this method does not strictly satisfy the inf-sup condition, it reduces constraints sufficiently to provide optimal convergence rates for the problems studied here.}

>>>>

\begin{abstract}
  In this paper we demonstrate the use of B\'{e}zier projection to alleviate locking phenomena in structural mechanics applications of isogeometric analysis. \added{Interpreting the well-known $\bar{B}$ projection in two different ways we develop two formulations for locking problems in beams and nearly incompressible elastic solids.  One formulation leads to a sparse symmetric symmetric system and the other leads to a sparse non-symmetric system.} To demonstrate the utility of \added{\Bezier projection} for both geometry and material locking phenomena we focus on transverse shear locking in Timoshenko beams and volumetric locking in nearly compressible linear elasticity although the approach can be applied generally to other types of locking phenemona as well. B\'{e}zier projection is a local projection technique with optimal approximation properties, which in many cases produces solutions that are comparable to global $L^2$ projection. In the context of $\bar{B}$ methods, the use of B\'ezier projection produces sparse stiffness matrices with only a slight increase in bandwidth when compared to standard displacement-based methods. Of particular importance is that the approach is applicable to any spline representation that can be written in B\'ezier form like NURBS, T-splines, LR-splines, etc. We discuss in detail how to integrate this approach into an existing finite element framework with minimal disruption through the use of B\'ezier extraction operators and a newly introduced dual \added{basis for} the \Bezier \added{projection} operator. We then demonstrate the behavior of the two proposed formulations through several challenging benchmark problems.
\end{abstract}
\keywords{Isogeometric analysis, B\'ezier extraction, \added{\Bezier dual basis}, B\'ezier projection, $\bar{B}$-projection, locking}
\section{Introduction}
Isogeometric analysis (IGA), introduced by Hughes et al. \cite{hughes_isogeometric_2005}, adopts the spline basis, which underlies the CAD geometry, as the basis for analysis. Of particular importance is the positive impact of smoothness on numerical solutions, where, in many application domains, IGA outperforms classical finite elements~\cite{cottrell_isogeometric_2009,cottrell_studies_2007,cottrell2006isogeometric,hughes_duality_2008,bazilevs_isogeometric_2010,evans_n-widths_2009}. Initial investigations of IGA focused on non-uniform rational B-splines (NURBS) due to their dominance in commercial CAD packages. However, many advances are being made in analysis-suitable geometry representations that overcome the strict rectangular topological restrictions of NURBS. Examples include T-splines~\cite{bazilevs_isogeometric_2010,sederberg_t-splines_2003} and their analysis-suitable restriction~\cite{scott_local_2012, li_analysis-suitable_2013}, hierarchical B-splines~\cite{bornemann_subdivision-based_2013,scott_isogeometric_2014,schillinger_isogeometric_2012,evans_hierarchical_2015,forsey_hierarchical_1988}, and locally refined B-splines~\cite{dokken_polynomial_2013,johannessen_isogeometric_2014} among others.

@@

\added{In this paper we introduce two methods that employ \Bezier projection to produce a localized approximation to the standard $\bar{B}$ method. The motivation behind these methods is the fact that $\bar{B}$ methods result in dense linear systems. The methods we introduce result in a sparse linear system irrespective of the choice of basis functions. We call these two methods the symmetric and non-symmetric \Bezier $\bar{B}$ projection methods, where the names indicate the symmetry of the resulting stiffness matrix. We show that both methods result in a sparse stiffness matrix and reduce locking. We also show that optimal convergence rates are achieved in the case of the non-symmetric method and near optimal convergence rates are achieved in the case of the symmetric method.  We also perform an inf-sup analysis of these methods.}

@@

\subsection{Symmetric \Bezier $\bar{B}$ projection}
\label{sec:symmetric-projection}
{\color{blue}Locking is caused in Timoshenko beam problems when equal order interpolation is used for both midline displacements and rotations. To reduce the effects of locking for these problems the $\bar{B}$ method projects the shear strain, $\gamma$, onto a lower order function space. This process produces a projected shear strain, which we call $\bar{\gamma}$,  that is substituted into the weak form of the problem statement. In this section we use the \Bezier projection operator to compute an approximation of $\bar{\gamma}$, and refer to this approach as the symmetric \Bezier $\bar{B}$ projection method because the resulting stiffness matrix is symmetric.}

@@

Localizing to the B\'{e}zier element we define the strain-displacement arrays in terms of element Bernstein basis functions of degree $p$ and $p-1$ as
\begin{align}
	\mathbf{B}_e^\kappa 
    	&= \begin{bmatrix} 0 & -{B^e_{0,p}}' & \cdots & 0 & -{B^e_{p,p}}' \end{bmatrix}, \\
    \mathbf{B}_e^\gamma
    	&= \begin{bmatrix} {B^e_{0,p}}' & -B^e_{0,p} & \cdots & {B^e_{p,p}}' & -B^e_{p,p} \end{bmatrix}, \\
    \bar{\mathbf{B}}_e
    	&= \begin{bmatrix} \bar{B}^e_{0,p-1} & \cdots & \bar{B}^e_{p-1,p-1} \end{bmatrix},
\end{align}
\added{where $B^e_{i,p}$ is the $i^{th}$ Bernstein basis function of order $p$}. We can then compute the element arrays as
\begin{align}
\mathbf{K}_e^b &= EI\mathbf{C}^e\langle{{\mathbf{B}_e^\kappa}^T,\mathbf{B}_e^\kappa}\rangle(\mathbf{C}^e)^T, \label{eq:symmetric_timoshenko}\\
\bar{\mathbf{M}}_e &= s{GA}\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\bar{\mathbf{B}}_e}\rangle(\bar{\mathbf{C}}^e)^T, \\
{\hat{\mathbf{P}}_e} &= \langle{(\hat{\bar{\mathbf{N}}}^e)^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T \label{eq:P-hat-elem},
\end{align}
where $\mathbf{C}^e$ is the element extraction operator for the degree $p$ spline space, $\bar{\mathbf{C}}^e$ is the element extraction operator for the degree $p-1$ spline space, and $\hat{\bar{\mathbf{N}}}^e$ are the dual basis functions restricted to the element for the degree $p-1$ spline space. The global stiffness matrix can then be written as
\begin{align}
	\mathbf{K} = \mathbf{K}^b + \bar{\mathbf{K}}^s_S \label{eqn:symmetric_b_bar_timoshenko_stiffness}
\end{align}
where
\begin{align}
	\mathbf{K}^b &=\A_e\mathbf{K}_e^b,\label{eqn:bending_stiffness} \\
	\bar{\mathbf{K}}^s&={\hat{\mathbf{P}}}^T\bar{\mathbf{M}}{\hat{\mathbf{P}}}\label{eqn:shear_stiffness} \\
	{\hat{\mathbf{P}}} &=\A_e{\hat{\mathbf{P}}_e} \label{eq:P-hat-global}\\
    \bar{\mathbf{M}} &=\A_e\bar{\mathbf{M}}_e
\end{align}
and $\A$ is the standard finite element assembly operator \cite{hughes_finite_2012}. We note that the assembly of $\bar{\mathbf{K}}^s$ requires the assembly of two intermediate matrices, $\bar{\mathbf{M}}$ and ${\hat{\mathbf{P}}}$. The computation of these matrices is needed because the product of two integrals over the entire domain can not be localized to the element level.
\subsection{Non-symmetric \Bezier $\bar{B}$ projection}
\label{sec:non-symmetric}

\added{Simo and Hughes \cite{hughes_variational_1986} have shown that $\bar{B}$ formulations and mixed formulations are equivalent. However, the development of the symmetric \Bezier $\bar{B}$ projection method presented in Section~\ref{sec:symmetric-projection}, where we began by interpreting the $\bar{B}$ formulation as a strain projection method, lacks a connection to mixed formulations. In this section, we present a second method based on \Bezier projection in which we view the $\bar{B}$ formulation as a mixed formulation where, for the Timoshenko beam problem, the auxiliary variable is the shear strain.  We use the \Bezier dual basis functions as the test functions for the auxiliary variable. Once the problem has been cast as a mixed formulation we then eliminate the auxiliary variable to get a purely displacement based formulation. This approach preserves convergence rates and all assembly routines for the stiffness matrix can be performed at the element level. However, it does not produce a symmetric stiffness matrix.}

\subsubsection{The weak form}
\added{In the mixed formulation for the Timoshencko beam problem the shear stress, $\tau=sGA\gamma$, is taken as a new independent variable. The weak form of the mixed formulation can then be stated as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ and $\tau\in{L}^2(\Omega)$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$ and $\delta\tau\in{L}^2(\Omega)$}
\begin{align}
    \int_{0}^L\kappa(\mathbf{w})EI\kappa(\mathbf{u}) + {\gamma}(\mathbf{w})\tau \, dx&= l\langle{\mathbf{w}}\rangle\\
    \int_{0}^L\delta\tau(sGA\gamma(\mathbf{u})-\tau) \, dx &= 0.
\end{align}
\subsubsection{Discretization}
\added{In the finite element formulation of the mixed problem, the discretization of $\mathbf{u}$ and $\mathbf{w}$ remain the same as before. The shear strain and its variation, however, are in $L^2(\Omega)$, so their finite element approximation can consist of functions with lower regularity, such as discontinuous polynomials. When the field $\mathbf{u}$ is discretized by $p^{th}$ degree spline basis functions defined by the knot vector given in \eqref{eq:origin_knot_vector}, we use the $p-1$ degree spline basis functions, defined by the knot vector given in \eqref{eq:projected_knot_vector}, to discretize the shear stress $\tau$ and the corresponding dual basis to discretize its variation $\delta\tau$. The discrete form of the shear stress and its variation are given by}
\begin{align}
    \tau&=\sum_A\tau_A\bar{N}_A \\
    \delta\tau&=\sum_A\delta\tau_A\hat{\bar{N}}_A.
\end{align}
\added{The stiffness matrix for the mixed form can then be written as}
\begin{equation}
   \mathbf{K}_{mix} =  
    \begin{bmatrix}
        \mathbf{K}^b & \mathbf{P}^T \\
        sGA\hat{\mathbf{P}} & -\mathbf{I}
    \end{bmatrix}
    \label{eq:mixed_timoshenko}
\end{equation}
\added{where}
\begin{equation}
    \mathbf{P}=\A_e\mathbf{P}_e,
\end{equation}
\added{and}
\begin{equation}
    \mathbf{P}_e=\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T.
\end{equation}
\added{ and $\hat{\mathbf{P}}$ is given in \eqref{eq:P-hat-elem} and \eqref{eq:P-hat-global}.
We can now eliminate the control variable of the shear stress from \eqref{eq:mixed_timoshenko} to get a pure displacement formulation where the stiffness matrix can be written as}
\begin{equation}
    \mathbf{K}=\mathbf{K}^b+\bar{\mathbf{K}}^s_{NS}, 
\end{equation}
where 
\begin{equation}
    \bar{\mathbf{K}}^s_{NS}=sGA\mathbf{P}^T\hat{\mathbf{P}}.
    \label{eq:nonsymmetric_timoshenko}
\end{equation}
\added{We can see that the use of different function spaces for the shear strain and its variation leads to a non-symmetric stiffness matrix.}

\paragraph{Remark} \added{ As mentioned previously, the symmetric \Bezier $\bar{B}$ formulation is not consistent with a mixed formulation. To see this, we can recover the mixed formulation of \eqref{eqn:symmetric_b_bar_timoshenko_stiffness}, which is}
\begin{equation}
    \begin{bmatrix}
        \mathbf{K}^b & \hat{\mathbf{P}}^T \\
        sGA\hat{\mathbf{P}} & -\bar{\mathbf{M}}^{-1}
    \end{bmatrix},
\end{equation}
\added{where both the shear stress and its variation are discretized by the dual basis functions. However, for the inner product of dual basis functions we have}
\begin{equation}
    \langle{\hat{\bar{N}}_i,\hat{\bar{N}}_j}\rangle\neq{\bar{\mathbf{M}}^{-1}_{ij}},
\end{equation}
\added{which shows the inconsistency between the symmetric \Bezier $\bar{B}$ formulation and the mixed formulation.}

@@

\section{Volumetric locking: Nearly incompressible linear elasticity}
\label{sec:nearlyincompressible}
To demonstrate the use of \Bezier $\bar{B}$ {methods} to alleviate volumetric locking effects we study the nearly incompressible elasticity problem in two dimensions. We start with the small strain tensor $\boldsymbol{\varepsilon}$, which is defined as the symmetric part of the displacement gradient, i.e., 
\begin{equation}
\varepsilon_{ij}=\dfrac{u_{i,j}+u_{j,i}}{2}.
\end{equation}
The stress tensor is related to the strain tensor through the generalized Hooke's law
\begin{equation}
\sigma_{ij}=c_{ijkl}\varepsilon_{kl}
\end{equation}
where, for isotropic elasticity, the elastic coefficients and stress tensor can be expressed in terms of the Lam\'{e} parameters $\lambda$ and $\mu$ as
\begin{align}
c_{ijkl} &=\mu(\delta_{ik}\delta_{jl}+\delta_{il}\delta_{jk})+\lambda\delta_{ij}\delta_{kl}\\
\sigma_{ij} &= \lambda\varepsilon_{kk}\delta_{ij} + 2\mu\varepsilon_{ij}.
\end{align}
The Lam\'e parameters $\lambda$ and $\mu$ are defined in terms of Young's modulus, $E$, and Poisson's ratio, $\nu$, as
\begin{align}
\lambda &=\dfrac{\nu{E}}{(1+\nu)(1-2\nu)}\\
\mu &=\dfrac{\nu{E}}{2(1+\nu)}.
\end{align}
we can write the strong form of linear elasticity as
\begin{align}
	\sigma_{ij,j}+f_i &= 0 \text{ in $\Omega$} \\
    u_i &= g_i\text{ on $\Gamma_{g_i}$} \\
    \sigma_{ij}n_j &= h_i\text{ on $\Gamma_{h_i}$}
\end{align}
where Dirichlet boundary conditions are applied on $\Gamma_{g_i}$, Neumann boundary conditions are applied on $\Gamma_{h_i}$, and the closure of the domain $\Omega$ is $\bar{\Omega}=\Omega\cup\Gamma_{g_i}\cup\Gamma_{h_i}$. \added{To demonstrate the source of volumetric locking, we introduce the pressure term}
\begin{equation}
    p=-(\lambda+2\mu/3){\epsilon}_{ii}.
\end{equation}
If $\nu\rightarrow\dfrac{1}{2}$ then $\lambda$ becomes very large and \added{the additional constraint $\epsilon_{ii} = 0$ is applied to the volumetric strain.}

\subsection{Symmetric \Bezier $\bar{B}$ projection}
\subsubsection{The weak form}
The $\bar{B}$ approach for nearly incompressible linear elasticity splits the strain tensor $\varepsilon$ into volumetric and deviatoric strains and then replaces the volumetric strain with a projected strain. We begin with
\begin{equation}
\boldsymbol{\varepsilon}(\mathbf{u})=\boldsymbol{\varepsilon}^{vol}(\mathbf{u})+\boldsymbol{\varepsilon}^{dev}(\mathbf{u})
\end{equation}
where $\boldsymbol{\varepsilon}^{vol}=\dfrac{1}{3}\mathrm{tr}(\boldsymbol{\varepsilon})\mi$ is the volumetric strain and $\boldsymbol{\varepsilon}^{dev}=\boldsymbol{\varepsilon}-\dfrac{1}{3}\mathrm{tr}(\boldsymbol{\varepsilon})\mi$ is the deviatoric strain. The volumetric strain is then replaced by a projected volumetric strain $\bar{\boldsymbol{\varepsilon}}^{vol}$ and the new total strain becomes
\begin{equation}
\bar{\boldsymbol{\varepsilon}}=\bar{\boldsymbol{\varepsilon}}^{vol}+\boldsymbol{\varepsilon}^{dev}.
\end{equation}
The weak form can then be written as: find $\mathbf{u}\in{\mathcal{S}(\Omega)}$ such that for all $\mathbf{w}\in{\mathcal{V}(\Omega)}$
\begin{equation}
    \bar{a}\langle{\mathbf{w},\mathbf{u}}\rangle=\bar{l}\langle{\mathbf{w}}\rangle
\end{equation}
where
\begin{align}
    \bar{a}\langle{\mathbf{w},\mathbf{u}}\rangle&=\int_{\Omega}\bar{\epsilon}_{ij}(\mathbf{w})c_{ijkl}\bar{\epsilon}_{kl}(\mathbf{u})d\Omega, \\
    \bar{l}\langle{\mathbf{w}}\rangle&=\int_{\Omega}\mathbf{w}\cdot\mathbf{f}d\Omega+\int_{\Gamma_{h}}\mathbf{w}\cdot\mathbf{h}d\Gamma.
\end{align}

@@

We have presented two B\'{e}zier $\bar{B}$ projection methods, which we have called symmetric and non-symmetric \Bezier $\bar{B}$ projection, as an approach to overcome locking phenomena in structural mechanics applications of isogeometric analysis. Each approach maintains the sparsity of the resulting linear system. The methods utilize B\'ezier extraction and projection, which makes it simple to implement them in an existing finite element framework and makes it applicable to any spline representation which can be written in \Bezier form. In contrast to global $\bar{B}$ methods, which produce dense stiffness matrices, the B\'ezier $\bar{B}$ approach results in a sparse stiffness matrix while still benefiting from higher-order convergence rates. \added{We have made the connection between the non-symmetric method and a mixed formulation and shown that, although this method does not strictly satisfy the inf-sup condition, it reduces constraints sufficiently to provide optimal convergence rates for the problems studied here.}
